### 2014-07-29 paper/paper.tex
preparing camera ready. bios to be updated before submitting final files
bio updated

\begin{figure} [!t]
	\begin{center}
	\includegraphics[scale=0.4,natwidth=708,natheight=484]{img/mcts.png}
	\caption{MCTS algorithm steps.}
	\label{fig:mcts}
	\end{center}
\end{figure}

@@

\begin{figure} [!t]
	\begin{center}
	\includegraphics[scale=0.235]{img/moopDec2.png}
	\caption{Decision and objective spaces in a MOP with two variables ($x_1$ and $x_2$) and two objectives ($f_1$ and $f_2$). In the objective space, yellow dots are non-optimal objective vectors, while blue dots form a non-dominated set. From~\cite{Brockhoff2013}.}
	\label{fig:moop}
	\end{center}
\end{figure}

@@

\begin{figure}[!t]
\begin{center}
\includegraphics[width=0.75\columnwidth]{img/hv}
\end{center}
\caption{$HV(P)$ of a given Pareto-front $P$}
\label{fig:hv}
\end{figure}

@@

\begin{figure}[!t]
\begin{center}
\includegraphics[width=0.65\columnwidth]{img/wangHV}
\end{center}
\caption{$r^p_x$ is the projection of the $r_x$ value on the piecewise linear surface (discontinuous line). The shadowed surface represents $HV(P)$. From~\cite{Weijia2012}.}
\label{fig:wangHV}
\end{figure}

@@

\begin{figure}[!t]
\begin{center}
\includegraphics[width=0.75\columnwidth]{img/dst}
\end{center}
\caption{Environment of the Deep Sea Treasure (from~\cite{Vamplew2010}): grey squares represent the treasure (with their different values) available in the map. The black cells are the sea floor and the white ones are the positions that the vessel can occupy freely. The game ends when the submarine picks one of the treasures.}
\label{fig:dstBase}
\end{figure}

@@

\begin{figure}[!t]
\begin{center}
\includegraphics[width=1.0\columnwidth]{img/optDST.png}
\end{center}
\caption{Optimal Pareto Front of the Deep Sea Treasure, with both objectives to be maximized.}
\label{fig:optDst}
\end{figure}

@@

\begin{figure}[!t]
\begin{center}
\includegraphics[width=0.9\columnwidth]{img/dstTransTables}
\end{center}
\caption{Example of two different sequences of actions (R: Right, D: Down) that lie in the same position in the map, but at a different node in the tree.}
\label{fig:dstTable}
\end{figure}

@@

\begin{figure} [!t]
	\begin{center}
	\includegraphics[width=0.8\columnwidth]{img/moptspmap}
	\caption{Sample MO-PTSP map.}
	\label{fig:sampleMap}
	\end{center}
\end{figure}

@@

\begin{figure*}[!t]
	\centering
	\includegraphics[width=2.1\columnwidth]{img/dstAll}
	\caption{Results in DST: percentages of each optima found during $100$ games played with different weight vectors. Scalarization approaches converge to the edges of the optimal front, whereas Pareto approaches are able to find all optimal solutions. The proposed algorithm, MO-MCTS, finds these solutions significantly more often than NSGA-II.}
	\label{fig:extCase}
\end{figure*}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/perez.jpg}}]
{Diego Perez}
is currently pursuing a Ph.D. in Artificial Intelligence applied to games at the University of Essex, Colchester. He has published in the domain of Game AI, participated in several Game AI competitions and organized the Physical Travelling Salesman Problem competitions, held in IEEE conferences. He also has programming experience in the videogames industry with titles published for game consoles and PC.
\end{IEEEbiography}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./photos/spyro.jpg}}]{Spyridon Samothrakis}
 is currently pursuing a PhD in Computational Intelligence and Games at the University of Essex. His interests include game theory, computational neuroscience, evolutionary algorithms and consciousness. 
\end{IEEEbiography}

>>>>

\begin{figure} [!t]
	\begin{center}
	\includegraphics[scale=0.4,natwidth=708,natheight=484]{figures/perez1.png}
	\caption{MCTS algorithm steps.}
	\label{fig:mcts}
	\end{center}
\end{figure}

@@

\begin{figure} [!t]
	\begin{center}
	\includegraphics[scale=0.235]{figures/perez2.png}
	\caption{Decision and objective spaces in a MOP with two variables ($x_1$ and $x_2$) and two objectives ($f_1$ and $f_2$). In the objective space, yellow dots are non-optimal objective vectors, while blue dots form a non-dominated set. From~\cite{Brockhoff2013}.}
	\label{fig:moop}
	\end{center}
\end{figure}

@@

\begin{figure}[!t]
\begin{center}
\includegraphics[width=0.75\columnwidth]{figures/perez3}
\end{center}
\caption{$HV(P)$ of a given Pareto-front $P$}
\label{fig:hv}
\end{figure}

@@

\begin{figure}[!t]
\begin{center}
\includegraphics[width=0.65\columnwidth]{figures/perez4}
\end{center}
\caption{$r^p_x$ is the projection of the $r_x$ value on the piecewise linear surface (discontinuous line). The shadowed surface represents $HV(P)$. From~\cite{Weijia2012}.}
\label{fig:wangHV}
\end{figure}

@@

\begin{figure}[!t]
\begin{center}
\includegraphics[width=0.75\columnwidth]{figures/perez5}
\end{center}
\caption{Environment of the Deep Sea Treasure (from~\cite{Vamplew2010}): grey squares represent the treasure (with their different values) available in the map. The black cells are the sea floor and the white ones are the positions that the vessel can occupy freely. The game ends when the submarine picks one of the treasures.}
\label{fig:dstBase}
\end{figure}

@@

\begin{figure}[!t]
\begin{center}
\includegraphics[width=1.0\columnwidth]{figures/perez6}
\end{center}
\caption{Optimal Pareto Front of the Deep Sea Treasure, with both objectives to be maximized.}
\label{fig:optDst}
\end{figure}

@@

\begin{figure}[!t]
\begin{center}
\includegraphics[width=0.9\columnwidth]{figures/perez7}
\end{center}
\caption{Example of two different sequences of actions (R: Right, D: Down) that lie in the same position in the map, but at a different node in the tree.}
\label{fig:dstTable}
\end{figure}

@@

\begin{figure} [!t]
	\begin{center}
	\includegraphics[width=0.8\columnwidth]{figures/perez8}
	\caption{Sample MO-PTSP map.}
	\label{fig:sampleMap}
	\end{center}
\end{figure}

@@

\begin{figure*}[!t]
	\centering
	\includegraphics[width=2.1\columnwidth]{figures/perez9}
	\caption{Results in DST: percentages of each optima found during $100$ games played with different weight vectors. Scalarization approaches converge to the edges of the optimal front, whereas Pareto approaches are able to find all optimal solutions. The proposed algorithm, MO-MCTS, finds these solutions significantly more often than NSGA-II.}
	\label{fig:extCase}
\end{figure*}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/perez.jpg}}]
{Diego Perez}
is currently pursuing a Ph.D. in Artificial Intelligence applied to games at the University of Essex (UK). He has published in the domain of Game AI, with research interests on Reinforcement Learning and Evolutionary Computation. He has organized several Game AI competitions, as the Physical Travelling Salesman Problem and the General Video Game AI competitions, both held in IEEE conferences. He also has programming experience in the videogames industry with titles published for game consoles and PC.
\end{IEEEbiography}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./photos/spyro.jpg}}]{Spyridon Samothrakis}
 is currently a Senior Research Officer at the University of Essex. He holds a B.Sc. from the University of Sheffield (Computer Science), an M.Sc. from the University of Sussex (Intelligent Systems) and a Ph.D (Computer Science) from the University of Essex. His interests include game theory, machine learning, evolutionary algorithms and consciousness.
\end{IEEEbiography}
